---
title: "HW04"
author: "Geraldo B. Padilla F."
date: "31-03-2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# HW04 using R

# set width of output and number of digits to be printed
options("width"=120, "digits"=8)
# turn off stars for different alpha levels
options(show.signif.stars=FALSE)

# Use this to turn off scientific notation: 
# "fixed notation will be preferred unless it is more than 'scipen' digits wide"
options(scipen=9)

#####  Check to see if packages are downloaded, install if not, then load  #####

```{r, message=FALSE}
library(readxl) # To import xls or xlsx data as table
library(expss) # To add variable and value labels, sorting
library(psych) # To add descriptive summary functions
library(multcomp) # To do glht linear combinations in GLMs
library(margins) # To get predicted values like Stata does
library(MASS) # To fit negative binomial model easily
library(TeachingDemos) # To create text output files
library(tidyverse)
```

# Import homework data and add labels
```{r}
HW04 <- read_excel("HW04/HW04_01445225.xlsx")
```

# Here are the variable labels (not to be included in data used)
FamilyID=   "FamilyID: Family ID"
HasYounger= "HasYounger: Has Younger Sibling (0=no, 1=yes)"
HasOlder=   "HasOlder: Has Older Sibling (0=no, 1=yes)"
BothWork=   "BothWork: Both Parents Work Full-Time (0=no 1=yes)"
FoodSchool= "FoodSchool: Number of Food School Sessions"
NumFoods=   "NumFoods: Number of New Foods Tried";

# Your code to center/recode predictors goes here

```{r}
HW04 <- HW04%>%
  mutate(
    if_any = ifelse(FoodSchool == 0, 0, 1), #any food school attendance
    atleast1 = ifelse(if_any == 1, FoodSchool - 1, 0)#number of food school sessions attended past one
  )
```

# Open output text file -- run this last if you want to save output
txtStart(file=paste0(filesave,"PSQF6270_HW04_Output.txt"))

# Your code to estimate models goes here

Section 1

```{r}
m0_p <- glm(NumFoods~1, family = poisson(link = 'log'), data = HW04)
summary(m0_p)
-2*logLik(m0_p); AIC(m0_p); BIC(m0_p)

DDFn=400     # What SAS uses
sum(residuals(m0_p, type="pearson")^2)/DDFn  # SAS

exp(m0_p$coefficients)

m0_nb <- glm.nb(NumFoods~1, link = log, data = HW04)
summary(m0_nb); -2*logLik(m0_nb)
AIC(m0_nb); BIC(m0_nb)

sum(residuals(m0_nb, type = 'pearson')^2)/DDFn
exp(m0_nb$coefficients)

DevTest = -2*(logLik(m0_p)-logLik(m0_nb))
RegPvalue = pchisq((DevTest), df=1, lower.tail=FALSE)
MixPvalue = RegPvalue/2
DevTest; RegPvalue; MixPvalue
```

Section 2

```{r}
m1_nb <- glm.nb(NumFoods~1+HasOlder+HasYounger+if_any+atleast1+BothWork+
                  BothWork:if_any+BothWork:atleast1,
                link = log, data = HW04)
summary(m1_nb)
-2*logLik(m1_nb)
AIC(m1_nb); BIC(m1_nb)

DDFn=400     # What SAS uses
sum(residuals(m1_nb, type="pearson")^2)/DDFn  # SAS

exp(cbind(m1_nb$coefficients))

summary(glht(m1_nb, linfct = rbind(
  'Q16' = c(0,1,0,0,0,0,0,0),
  'Q17' = c(0,0,1,0,0,0,0,0),
  'Q20' = c(0,0,0,1,0,0,0,0),
  'Q21' = c(0,0,0,1,0,0,1,0),
  'Q22' = c(0,0,0,0,0,0,1,0),
  'Q24' = c(0,0,0,0,1,0,0,1),
  'Q26' = c(0,0,0,0,0,1,0,0),
  'Q27' = c(0,0,0,0,0,1,1,0),
  'Q28' = c(0,0,0,0,0,1,1,2),
  'Q29' = c(0,0,0,0,0,1,1,4),
  'Q30' = c(0,0,0,0,0,0,1,0),
  'Q31' = c(0,0,0,0,0,0,0,1))),
  test = adjusted('none'))

summary(m1_nb)

summary(prediction(m1_nb, type="response", at=list(HasOlder=0,HasYounger=0,if_any=0,atleast1=0,BothWork=1)))$Prediction

summary(prediction(m1_nb, type="response", at=list(HasOlder=0,HasYounger=0,if_any=1,atleast1=c(0,2,4),BothWork=c(0,1))))
```

Section 3

```{r}
m1_p <- glm(NumFoods~1+HasOlder+HasYounger+if_any+atleast1+BothWork+
                  BothWork:if_any+BothWork:atleast1, family = poisson(link = 'log'), data = HW04)
summary(m1_p)
-2*logLik(m1_p)
AIC(m0_p); BIC(m0_p)

DDFn=400     # What SAS uses
sum(residuals(m1_p, type="pearson")^2)/DDFn  # SAS

DevTest = -2*(logLik(m1_p)-logLik(m1_nb))
RegPvalue = pchisq((DevTest), df=1, lower.tail=FALSE)
MixPvalue = RegPvalue/2
DevTest; RegPvalue; MixPvalue
```