---
title: "HW05"
author: "Geraldo B. Padilla F."
date: "19-04-2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Set width of output and number of digits to be printed
options("width"=120, "digits"=8)
# Turn off stars for different alpha levels
options(show.signif.stars=FALSE)

# Use this to turn off scientific notation: 
# "fixed notation will be preferred unless it is more than 'scipen' digits wide"
options(scipen=9)

## Packages
```{r}
library(readxl)
library(expss)
library(psych)
library(multcomp)
library(margins)
library(nlme)
library(emmeans)
library(lavaan)
library(TeachingDemos)
```

# Import homework data and add labels

```{r}
HW05 <- read_excel("HW05/HW05_01445225.xlsx")
```

# Here are the variable labels (not to be included in data used)
# PersonID=   "PersonID: Person ID number"
# Training=   "Training: Training Type 1=Pancake, 2=Crepe"
# Experience= "Experience: Experience with Food of Training"
# Rating1=    "Rating1: Rating of Pancakes Outcome"
# Rating2=    "Rating2: Rating of Crepes Outcome"

# Your code to stack data into long and then center/recode predictors goes here

```{r}

```

# Your code to estimate models goes here

```{r}

```