---
title: "HW05"
author: "Geraldo B. Padilla F."
date: "19-04-2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Set width of output and number of digits to be printed
options("width"=120, "digits"= 6)
# Turn off stars for different alpha levels
options(show.signif.stars=FALSE)

# Use this to turn off scientific notation: 
# "fixed notation will be preferred unless it is more than 'scipen' digits wide"
options(scipen=9)

## Packages
```{r, message=FALSE, warning=FALSE}
library(readxl)
library(expss)
library(psych)
library(multcomp)
library(margins)
library(nlme)
library(emmeans)
library(lavaan)
library(TeachingDemos)
library(tidyverse)
```

# Import homework data and add labels

```{r}
d1 <- read_excel('C:/Users/Lenovo/OneDrive - University of Iowa/PhD portfolio/2. Courses/2. Spring 2022/PSQF62700001 Generalized Linear Models (Lesa Hoffman)/4. Homeworks/HW05/HW05_01445225.xlsx')
```

Here are the variable labels (not to be included in data used)

# PersonID=   "PersonID: Person ID number"
# Training=   "Training: Training Type 1=Pancake, 2=Crepe"
# Experience= "Experience: Experience with Food of Training"
# Rating1=    "Rating1: Rating of Pancakes Outcome"
# Rating2=    "Rating2: Rating of Crepes Outcome"

# Your code to stack data into long and then center/recode predictors goes here

```{r}
d1 <- d1%>%
  pivot_longer(Rating1:Rating2, names_to = 'ratings', values_to = 'score')

d1 <- d1%>%
  mutate(
    group = ifelse(Training == 1 & ratings == 'Rating1', 0,
                   ifelse(Training == 1 & ratings == 'Rating2',1,
                          ifelse(Training == 2 & ratings == 'Rating1',2,3))),
    rating = ifelse(ratings == 'Rating1', 1, 2),
    g1 = ifelse(Training == 1 & ratings == 'Rating1', 1,0),
    g2 = ifelse(Training == 1 & ratings == 'Rating2',1,0),
    g3 = ifelse(Training == 2 & ratings == 'Rating1',1,0),
    g4 = ifelse(Training == 2 & ratings == 'Rating2',1,0))
```

# Your code to estimate models goes here

Section 1

```{r}
m0 <- gls(d1,method="REML", 
              model=score~0+factor(rating),
              correlation=corSymm(form=~rating|PersonID),
              weights=varIdent(form=~1|rating))

-2*logLik(m0)
summary(m0)

#R and RCORR matrices
getVarCov(m0, individual="1")
corMatrix(m0$modelStruct$corStruct)[[3]]

#DV means, pairwise mean differences, and omnibus F-test
emmeans(ref_grid(m0), pairwise~rating, adjust="none")
joint_tests(m0)
```

Section 2

```{r}
m1 <- gls(d1,method="REML", 
              model=score~0+factor(group),
              correlation=corSymm(form=~rating|PersonID),
              weights=varIdent(form=~1|rating))

-2*logLik(m1)
summary(m1)

#R and RCORR matrices
getVarCov(m1, individual="1")
corMatrix(m1$modelStruct$corStruct)[[3]]

#DV means, pairwise mean differences, and omnibus F-test
emmeans(ref_grid(m1), pairwise~group, adjust="none")
joint_tests(m1)

#estimate for the difference in the above between-person training effects (Q27 vs Q29) for pancake vs. crepe outcomes
summary(glht(model=m1, df=996 , linfct=rbind(
  "pancake vs. crepe" = c(0,-1,0,1) - c(1,0,-1,0))), test=adjusted("none"))
```

Section 3

```{r}
m2 <- gls(d1,method="REML", model=score~0+g1+g2+g3+g4+
            g1:Experience+g2:Experience+g3:Experience+g4:Experience,
          correlation=corSymm(form=~rating|PersonID),
          weights=varIdent(form=~1|rating))

-2*logLik(m2)
summary(m2)
coef(m2)

#R and RCORR matrices
getVarCov(m2, individual="1")
corMatrix(m2$modelStruct$corStruct)[[3]]

#DV means, pairwise mean differences, and omnibus F-test
F2c = glht(model=m2, linfct=rbind(c(0,0,0,0),
                                  c(0,0,0,0)), df=992)
SaveF2c = summary(F2c, test=Ftest()); SaveF2c # Joint F-test

#Get and show hidden results for F, dfnum, dfden, and p-value
SaveF0c$test$fstat; SaveF0c$test$df; SaveF0c$df
pf(SaveF0c$test$fstat,df1=SaveF0c$test$df,df2=SaveF0c$df,lower.tail=FALSE)


#estimate for the difference in slopes
summary(glht(model=m2, df=992, linfct=rbind(
  "Q37" = c(0,0,0,0,1,0,0,0),
  "Q39" = c(0,0,0,0,0,1,0,0),
  "Q41" = c(0,0,0,0,1,-1,0,0),
  "Q43" = c(0,0,0,0,0,0,1,0),
  "Q45" = c(0,0,0,0,0,0,0,1),
  "Q47" = c(0,0,0,0,0,0,-1,1),
  "Q49" = c(0,0,0,0,-1,0,0,1),
  "Q51" = c(0,0,0,0,0,1,-1,0))),test=adjusted("none"))
```