---
title: "HW03"
author: "Geraldo B. Padilla F."
date: "10-03-2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# HW03 using R

Set width of output and number of digits to be printed
```{r}
options("width"=120, "digits"=8)
```

Turn off stars for different alpha levels
```{r}
options(show.signif.stars=FALSE)
```

Use this to turn off scientific notation: 
"fixed notation will be preferred unless it is more than 'scipen' digits wide"
```{r}
options(scipen=9)
```

Check to see if packages are downloaded, install if not, then load  #####
```{r, message=FALSE}
library(readxl)
library(expss)
library(psych)
library(multcomp)
library(margins)
library(VGAM)
library(TeachingDemos)
library(dplyr)
```

Define variables for working directory and data name
```{r}
d1 <- data.frame(read_excel('HW03_01445225.xlsx'))
```

Here are the variable labels (not to be included in data used)

- FamilyID=      "FamilyID: Family ID"
- Income=        "Income: Annual Family Income in Dollars"
- Care=          "Care: Need After-School Child Care (0=no, 1=yes)"
- SchoolQuality= "SchoolQuality: 1=Low, 2=Medium, 3=High"
- SchoolChoice=  "SchoolChoice: 1=Public, 2=Montessori, 3=Private"

Your code to center/recode predictors goes here
```{r}
mean(d1$Income)
d1$Income_centered <- (d1$Income - 50000)/10000
count(d1, SchoolQuality)
```

Ordinal perceived school quality is predicted by additive effects of annual family income and need for after-school child care

Your code to estimate models goes here:

Ordinal outcome:
```{r}
#model subtracting 1 to the outcome variable, the result is the same
d1%>%
mutate(school = SchoolQuality - 1)%>%
  vglm(school~1, family = cumulative(link = 'logitlink', reverse = T, parallel = T), data = .)%>%
  summary()

m01 <- vglm(SchoolQuality~1, family = cumulative(link = 'logitlink', reverse = T, parallel = T), data = d1)
summary(m01); AIC(m01); BIC(m01) # Get AIC and BIC too

#comparing the observed and model implied means(probs)
m01Prob=1/(1+exp(-1*coefficients(m01))); m01Prob
prop.table(table(d1$SchoolQuality))

m1 <- vglm(SchoolQuality~1+ Income_centered + Care, family = cumulative(link = 'logitlink', reverse = T, parallel = T), data = d1)
summary(m1)

m2 <- vglm(SchoolQuality~1+Income_centered+Care, family = cumulative(link = 'logitlink', reverse = T, parallel = F), data = d1)
summary(m2)
```

Nominal outcome:
```{r}
prop.table(table(d1$SchoolChoice))

m3_empty <- vglm(SchoolChoice~1, family=multinomial(refLevel = 1), reverse=TRUE, data = d1)
summary(m3_empty)

1/(1+exp(-1*coefficients(m3_empty)))#from logodds to probs
.248/(.659+.248)
.093/(.659+0.093)

m3 <- vglm(SchoolChoice~1+Income_centered+Care, family = multinomial(refLevel = 1), reverse = T, data = d1)
summary(m3)
```

Odds Ratios
```{r}
exp(cbind(OR = coefficients(m1), confint(m1)))
exp(cbind(OR = coefficients(m2), confint(m2)))
exp(cbind(OR = coef(m3), confint(m3)))
```