---
title: "HW02"
author: "Geraldo B. Padilla F."
date: "16-02-2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# HW02 using R
```{r options, message=FALSE}
#set width of output and number of digits to be printed
options("width"=120, "digits"=8)
# turn off stars for different alpha levels
options(show.signif.stars=FALSE)
# Use this to turn off scientific notation: 
# "fixed notation will be preferred unless it is more than 'scipen' digits wide"
options(scipen=999)
```

## Check to see if packages are downloaded, install if not, then load
```{r packages, message=FALSE}
library(readxl) # To import xls or xlsx data as table
library(expss) # To add variable and value labels, sorting
library(psych) # To add descriptive summary functions
library(multcomp) # To do glht linear combinations in GLMs
library(margins) # To get predicted values like Stata does
library(TeachingDemos) # To create text output files
library(dplyr)
library(multcomp)
```

## Define variables for working directory and data name

```{r data.set}
setwd('C:/Users/Lenovo/OneDrive - University of Iowa/PhD portfolio/2. Courses/Spring 2022/PSQF62700001 Generalized Linear Models (Lesa Hoffman)/4. Homeworks/HM02')
data <- data.frame(read_excel("HW02_01445225.xlsx"))
```

## Here are the variable labels (not to be included in data used)
- PersonID=   "PersonID: Person ID"
- Npubs=      "Npubs: Number of Published Research Papers"
- Nposters=   "Nposters: Number of Conference Posters"
- QuantLevel= "QuantLevel: 1=Low, 2=Medium, 3=High"
- Job=        "Job: 0=No Job Offer, 1=Received Job Offer"

## Center/recode predictors goes here

```{r dummy}
data = data%>%
  mutate(
    Medium = ifelse(QuantLevel == 2, 1, 0),
    High = ifelse(QuantLevel == 3, 1, 0))
```

## Create fake people for use in generating predicted outcomes

```{r fake.people}
FP = data.frame(
  gpa3 = c(-1,0,1,-1,0,1,-1,0,1,-1,0,1),
  parD = c( 0,0,0, 0,0,0, 1,1,1, 1,1,1),
  priv = c( 0,0,0, 1,1,1, 0,0,0, 1,1,1))
```

## Models

```{r empty.model}
m0 <- glm(Job ~ 1, data = data, family = binomial(link = 'logit'));summary(m0)
m0_probs <- 1/(1+exp(-1*coef(m0))); m0_probs
```

```{r models}
m1 <- glm(Job ~ 1 + Npubs + Nposters, family = binomial(link = 'logit'), data = data)
summary(m1)
#BIC(m1) #get BIC too

m2 <- glm(Job ~ 1 + Npubs + Nposters + Medium + High, data = data, family = binomial(link = 'logit'))
summary(m2)

m3 <- glm(Job ~ 1 + Npubs + Nposters + Medium + High + Npubs:Medium + Npubs:High, data = data, family = binomial(link = 'logit'))
summary(m3)
```

## Odds of the coefficients
```{r odds}
#95% CIs
exp(cbind(OR = coef(m1))) #for m1
exp(cbind(OR = coef(m2)))
```

## Multivariate Wald Test

```{r wald.tests}
wald_m1 = glht(m1, linfct = c('Npubs=0', 'Nposters=0'))
#summary(wald_m1, test = Ftest()) # Joint F-test instead of separate
summary(wald_m1, test = Chisqtest()) # Joint chi-square test

wald_m2 <- glht(m2, linfct = c('Npubs=0', 'Nposters=0', 'Medium=0', 'High=0'))
summary(wald_m2, test = Chisqtest())

wald_improvement_m2 <- glht(m2, linfct = c('Medium=0', 'High=0'))
summary(wald_improvement_m2, test = Chisqtest())

wald_m3 <- glht(m3, linfct = c('Npubs=0', 'Nposters=0', 'Medium=0', 'High=0', 'Npubs:Medium=0', 'Npubs:High=0'))
summary(wald_m3, test = Chisqtest())

wald_improvement_m3 <- glht(m3, linfct = c('Npubs:Medium=0', 'Npubs:High=0'))
summary(wald_improvement_m3, test = Chisqtest())
```

## Main and Simples slopes
```{r slopes}
ms_m1 <- summary(glht(m1, linfct=rbind(
  "Nposters vs. Npubs" = c(0,1,-1))), test=adjusted("none"))
data.frame(OR=exp(ms_m1$test$coefficients)) #take the odds of the log diff.

(ms_m2 <- summary(glht(m2, linfct = rbind(
  'low vs. medium' = c(0,0,0,1,0),
  'low vs. high' = c(0,0,0,0,1),
  'medium vs. high' = c(0,0,0,-1,1),
  'Nposters vs. Npubs' = c(0,1,-1,0,0))), test = adjusted('none')))
data.frame(OR = exp(ms_m2$test$coefficients))

(sl_m3 <- summary(glht(m3, linfct = rbind(
  'Npubs at Low (Intercept)' = c(0,1,0,0,0,0,0),
  'Npubs at Medium' = c(0,1,0,0,0,1,0),
  'Npubs at High' = c(0,1,0,0,0,0,1),
  'Low (Intercept) vs. Medium' = c(0,0,0,0,0,1,0),
  'Low (Intercept) vs. High' = c(0,0,0,0,0,0,1),
  'Medium vs. High' = c(0,0,0,0,0,-1,1))), test = adjusted('none')))
data.frame(OR = exp(sl_m3$test$coefficients))
```

## Predicted probabilities
```{r}
# Yhat in logits for specific values of predictors
#Main2Logits = prediction(model=Model2Main, type="link", at=list(gpa3=-1:1,parD=0:1,priv=0:1))
#summary(Main2Logits)

# Yhat in probability for specific values of predictors
Probs_low = prediction(m3, type="response",
                        at=list(Npubs=c(2,4), Nposters=3, Medium=0, High=0))
summary(Probs_low)
Probs_medium = prediction(m3, type="response",
                        at=list(Npubs=c(2,4), Nposters=3, Medium=1, High=0))
summary(Probs_medium)
Probs_high = prediction(m3, type="response",
                        at=list(Npubs=c(2,4), Nposters=3, Medium=0, High=1))
summary(Probs_high)
```
